To log or not to log

### 2022-11-26 main.tex
Version before incorporating Seb's Feedback

Probabilistic forecasts play an important role in decision-making in epidemiology and public health \citep{reichCollaborativeMultiyearMultimodel2019, funkShorttermForecastsInform2020, cramerEvaluationIndividualEnsemble2021, bracherShorttermForecastingCOVID192021, europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}, as well as other areas as diverse as economics \citep{timmermannForecastingMethodsFinance2018, elliottForecastingEconomicsFinance2016} or meteorology \citep{gneitingWeatherForecastingEnsemble2005, kukkonenReviewOperationalRegionalscale2012}. Epidemiological modelling in particular has received widespread attention during the COVID-19 pandemic. Evaluations of forecasts can provide feedback for forecasters and researchers to improve their models, and help decision makers distinguish good from bad predictions and choosing forecasters and models that should inform future decisions.

Probabilistic forecasts \citep{heldProbabilisticForecastingInfectious2017} are usually evaluated using so-called proper scoring rules \citep{gneitingStrictlyProperScoring2007}, which return a numerical score as a function of the forecast and the observed data. Forecasters, in expectation, optimise their score by providing a predictive distribution that is equal to the data-generating distribution, and will be penalised if they fail to do so. 
This paper focuses on one particular proper scoring rule, the Weighted Interval Score (WIS, formulas given in Section \ref{wis} in the SI) \citep{bracherEvaluatingEpidemicForecasts2021}, which is commonly used in epidemiology and other fields. The WIS can be understood as an approximation of the Continuous Ranked Probability Score (CRPS) \citep{gneitingStrictlyProperScoring2007} for predictive distributions represented by a set of predictive quantiles. The WIS and the CRPS measure the absolute distance between the predictive distribution and the observed value and can be understood as a generalisation of the absolute error to full predictive distributions (see details in Sections \ref{wis} and \ref{crps} in the SI). For simplicity, we will use "absolute error" and "absolute distance" interchangeably, even though the former applies only to point forecasts and the latter is more appropriate for predictive distributions. 
The WIS has been and is currently used by several Forecast Hubs for COVID-19 in the US \citep{cramerCOVID19ForecastHub2020, cramerEvaluationIndividualEnsemble2021}, Europe \citep{sherrattPredictivePerformanceMultimodel2022}, Germany and Poland \citep{bracherShorttermForecastingCOVID192021, bracherNationalSubnationalShortterm2021}, as well as the US Flu Forecasting Hub \citep{CdcepiFlusightforecastdata2022}.

Epidemiological processes are commonly understood and modeled to be inherently exponential in nature, as every infectious individual is assumed to lead to some number of additional infections [CITATION]. 
Evaluating forecasts based on the absolute distance between forecast and observed value may therefore not be optimal in an epidemiological context, and it could be more appropriate to focus the evaluation on errors on the multiplicative growth rate, in order for the evaluation to better represent the underlying disease dynamics. Evaluating forecasts based on absolute, rather than relative errors, in practice also means that scores are strongly influenced by the overall order of magnitude of the quantity to forecast. This makes it difficult compare predictive performance across time, given that epidemiological processes may be non-stationary, or to compare performance across targets that are on very different orders of magnitudes (for example cases and hospitalisations) [CITE \citep{sherrattPredictivePerformanceMultimodel2022}, and others].

In this paper, we discuss how log transforming the forecasts and observations prior to applying the WIS (or CRPS) may be an appropriate way to address the aforementioned issues with evaluating forecasts based on absolute errors. We first outline the motivation for transforming forecasts prior to scoring (section [REF]). We then provide a mathematical intuition of the impact of scoring on the log scale and its interpretation (section [REF]). We illustrate our findings on a series of examples using forecasts submitted to the European COVID-19 Forecast Hub  \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. Finally, we give scoring recommendations, discuss alternative transformations that may be useful in different contexts, and suggest further research avenues on the use of transformed scores in the evaluation of infectious disease forecasts.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Log transforming forecasts and observations}

The goal of log transforming forecasts and observations is to shift the focus of the evaluation in a way that may more appropriate for epidemiological forecasts, while preserving the propriety of the score. Instead of a score representing the magnitude of absolute errors this approach makes it possible to obtain a score which a) measures relative error and b) provides an approximate measure for how well a forecast captures the multiplicative growth rate of the target quantity. Focusing on relative errors mitigates issues with scores based on absolute errors that are heavily influenced by the order of magnitude of the quantity to forecast. The interpretation of the log transformed score as an approximate score for a forecast of the growth rate of a given quantity aligns the evaluation with our understanding of how epidemiological processes should be modeled and the kinds of errors models would typically make [CITATION?]. In this paper we focus on the log transformation, but note that many other transformations may be useful and appropriate (see section \ref{sec:discussion}) .

@@

To illustrate the effects of applying the logarithm intuitively, let us consider a point forecast $\hat{y}_{t+1}$ for a quantity of interest $y_{t+1}$, such that 
\begin{equation}
y_{t+1} = \hat{y}_{t+1} + \varepsilon_{t+1}.
\end{equation}

The analogon of the WIS / CRPS for point forecasts is the absolute error, and so the score will be determined by the size of the forecast error $\varepsilon_{t+1}$. When taking the logarithm of the forecast and the observation first, then the score is determined based on the size of $\varepsilon^*_{t+1}$: 
\begin{equation}
\log y_{t+1} = \log \hat{y}_{t+1} + \varepsilon^*_{t+1}.
\end{equation}
%
It is easy to see that this corresponds to evaluating a multiplicative error on the original $y_{t+1}$:
%
\begin{align}
\log y_{t+1} &= \log \hat{y}_{t+1} + \varepsilon^*_{t+1} \Leftrightarrow \\    
y_{t+1} &= \hat{y}_{t+1} \cdot \exp{\varepsilon^*_{t+1}}.    
\end{align}
% %>%

@@

Note that the analogy between the WIS on the log scale and the absolute error of a point forecast on the log scale is slightly inaccurate: While the absolute error on the log scale is exactly symmetric (e.g., predicting 2 instead of 1 would give the same relative error as predicting 0.5), this is not entirely true for the WIS, which is computed for a set of prediction intervals. Due to the fact that upper and lower bounds of individual prediction intervals are affected slightly differently by the log transformations, small deviations may occur (compare e.g. in Figure \ref{fig:change-in-scores}D the small difference between scores for an observed outcome of $\frac{1}{5}$ and 5).

@@

Computing a score based on the logarithm of the forecast and the observation is also approximately equivalent to scoring a forecast of a multiplicative growth rate of the forecast target. The growth rate is defined as
%
\begin{equation}
    g_{t, t+1} = \frac{y_{t+1} - y_t}{y_t},
\end{equation}
%
where $y_{t+1}$ is the forecast target (e.g. reported cases of COVID-19) in the future, $y_t$ is the last known observation and $g_{t, t+1}$ is the growth rate between now ($t$) and $t+1$. 
Using the growth rate, we can express the value of the forecast target in the future as such: 
%
\begin{equation}
y_{t+1} = (1 + g_{t, t+1}) \cdot y_t.
\end{equation}
%

Now consider a forecast on $\log y_{t+1}$, where again, the score is determined by the size of $\varepsilon^*_{t+1}$. Using the fact that for small values of $x$, $\log (1+ x) \approx x$, we can see that scoring forecasts on the log scale is approximately equal to scoring an additive error on the growth rate (on the natural scale), as long as the growth rate is small.
%
\begin{align}
\log y_{t+1}        &= \log \hat{y}_{t+1} + \varepsilon^*_{t+1} \\
                    &= \log ((1 + \hat{g}_{t+1}) \cdot y_{t}) + \varepsilon^*_{t+1} \\
                    &= \log (1 + \hat{g}_{t, t+1}) + \log y_t + \varepsilon^*_{t+1} \Leftrightarrow \\
\\
\varepsilon^*_{t+1}  &= \log y_{t+1} -  \log y_t - \log (1 + \hat{g}_{t, t+1}) \\    
                    &= \log (\frac{y_{t+1}}{y_t}) - \log (1 + \hat{g}_{t, t+1}) \\    
                    &= \log (1 + g_{t, t+1}) - \log (1 + \hat{g}_{t, t+1}) \\   
                    &\approx g_{t, t+1} - \hat{g}_{t, t+1} \quad \text{for small differences between } \hat{g}_{t, t+1} \text{ and } g_{t, t+1}. 
\end{align}

@@

\subsection{Effects on model rankings}
Rankings between different forecasters may change through the log transformation both when looking at aggregate scores as well as when looking at a single forecast. As an example for the effect on a single forecast, consider two forecasters, A and B. Both issue a single 50\%-prediction interval for a target which later resolves as 1. Forecaster A issues the interval [0.5, 2], while forecaster B issues [0.9. 2.5]. On the natural scale, the score would equal the dispersion of the forecast, i.e. the length of this interval (since the observed value falls within the prediction interval). Forecaster A would receive a score of $2 - 0.5$ = 1.5, beating forecaster B who would receive a score of $2.5 - 0.9 = 1.6$. When we transform the forecast, forecaster A receives a score of $\log (\frac{2}{0.5}) = 1.39$, while forecaster B obtains a score of $\log (\frac{2.6}{0.9}) = 1.06$ and now wins over forecaster A. The main difference between forecaster A and B is that forecaster A has issued a prediction interval ([0.5, 2]) that was more symmetric around the true value than the interval issued by forecaster B ([0.9. 2.6], which was more skewed). This means that in relative terms, Forecaster B was noticeably closer to the true value with the lower bound of her prediction interval, while only being slightly further away with the upper interval. This implies that scores on the log scale may treat (one-sided) outlier forecasts more leniently.

% PARAGRAPH NEEDS SOME WORK
Overall model rankings usually differ even more when scores are averaged across multiple forecasts. The change in rankings of aggregate scores is not mainly driven by the kinds of changes in model rankings for single forecasts just discussed. Rather, as observations from exponential processes are likely to be on very different absolute scales, large observations will account for the majority of absolute score but will not dominate relative scores in the same way. When aggregating scores across metrics with different scales, for example reported cases, and hospitalisations, even an ideal (i.e. perfect) forecaster will make much larger errors when predicting case numbers than when predicting hospitalisations. Evaluating forecasts based on relative errors may help with comparing performance across different targets. However, log transforming forecasts and observations may also result in the opposite extreme, since small absolute errors (e.g. predicting 9, rather than 3 deaths) may be large in relative terms if the quantity to forecast is very small. This is especially true when forecasts are restricted to discrete values.

@@

The log transformation is permissible (in the sense that it preserves propriety of the score), because it is a strictly monotonic transformation. Even though actual rankings between models may change, a forecaster will in expectation still minimise her score if she reports a predictive distribution that is equal to the data-generating distribution. The order of the operations matters, and applying the log transformation after scores have been computed, i.e. computing $\log S(F, y)$ results in an improper score. This is because taking the logarithm of the WIS / CRPS results in a score that does not penalise outliers enough and therefore incentivises overconfident predictions. We illustrate this point using simulated data in Figure \ref{fig:log-improper}, where it can easily be seen that overconfident models perform best in terms of the log WIS.

@@

In practice, one issue with the log transformation is that it cannot readily be applied to negative numbers or zero values. In addition, it may difficult to reliably evaluate relative errors when dealing with small discrete values. In an epidemiological setting that involves count data, negative values should likely be omitted entirely. One solution to deal with zeroes and small values is to also exclude those from ongoing analysis. An alternative is to add a small quantity, such as 1, to all observations and predictions before taking the logarithm as is common practice when log transforming counts. This represents a strictly monotonic transformation and therefore preserves propriety of the resulting score. The choice of the number to add influences scores and rankings, as measures of relative errors shrink when adding a constant to the forecast and the observation. Adding something to the forecasts and observations changes scores for forecasts of small quantities most, as relative errors shrink more the smaller the original value before adding a constant. In principle, it would also be possible to exploit the difference in how scores are affected in order to equalise scores for forecasts of quantities across different scales by adding a larger number (e.g. 100 or 10,000) if average scores are dominated too strongly by forecasts for small quantities.

@@

As an empirical example for evaluating forecasts on the natural and on the log scale we use forecasts from the European Forecast Hub \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. 
The European COVID-19 Forecast Hub is one of several COVID-19 Forecast hubs (together with a Hub in the US \citep{cramerEvaluationIndividualEnsemble2021} and one in Germany and Poland \citep{bracherShorttermForecastingCOVID192021} that systematically collects, aggregated and evaluated forecasts of several COVID-19 targets created by different teams every week. Forecasts are made one to four weeks ahead into the future and follow a quantile-based format with a set of 22 quantiles plus the median ($0.01, 0.025, 0.05, ..., 0.5, ... 0.95, 0.975, 0.99$).

@@

In addition to the WIS we use pairwise comparisons \citep{cramerEvaluationIndividualEnsemble2021} to evaluate models against each other. In a first step, score ratios are computed for all pairs of models by taking the set of overlapping forecasts between the two models and dividing the score of one model over the score achieved by the other model. The relative skill for a given model is then obtained by taking the geometric mean of all score ratios which involve that model. Low values are better, and the average model receives a relative skill score of 1.

@@

Across the dataset, the average number of observed cases and deaths varied considerably by location and target type (see Figure \ref{fig:HUB-mean-locations}A and B). On the natural scale, scores also varied considerably across targets (see Fig \ref{fig:HUB-mean-locations}D) and locations (see Fig \ref{fig:HUB-mean-locations}C). On the log scale, scores were more evenly distributed between targets (see Fig \ref{fig:HUB-mean-locations}D) and locations (see Fig \ref{fig:HUB-mean-locations}). Both on the natural scale as well as on the log scale, scores increased considerably with increasing forecast horizon (see Figure \ref{fig:HUB-mean-locations}E). The increase was more pronounced for cases than for deaths. We hypothesise that this increase in scores across horizons represents the relative difficulty to forecast values into the future, which was noticeable both on the natural as well as the logarithmic scale.

@@

As expected on the natural scale, scores correlate strongly with the average number of observed cases and deaths (Spearman rank correlation: 0.96 and 0.97) in a given country (see Fig \ref{fig:HUB-mean-locations}A, B).
On the log scale correlation is much weaker and slightly negative, at least in terms of rank correlation (Spearman correlation: -0.33 and -0.36), implying larger scores for for countries with lower mean incidences.

@@

For \textit{individual} forecasts, rankings between models for single forecasts are mostly preserved, with differences increasing across forecast horizons (see Figure \ref{fig:HUB-cors}). When evaluating performance \textit{across} different forecasts and forecast targets, relative skill scores of the models change considerably. The change is stronger for cases than for deaths (Figure \ref{fig:HUB-cors}C) and tends to increase with increasing forecast horizon.

When comparing examples of forecasts on the natural scale with log-transformed ones (see Figures \ref{fig:HUB-model-comparison-ensemble}, \ref{fig:HUB-model-comparison-baseline}, \ref{fig:HUB-model-comparison-epinow}) a few interesting patterns emerge. Missing the peak, i.e. predicting increasing numbers while actual observations are already falling, tends to contribute a lot to overall scores on the natural scale (see forecasts in May in Figure \ref{fig:HUB-model-comparison-ensemble}A, B). On the log scale, these have less of an influence, as errors are smaller in relative terms (see panels C and D). We hypothesise that the larger divergence in scores for cases (compared to scores for deaths) displayed in Figure \ref{fig:HUB-pairwise}C is related to the fact that outlier forecasts missing the peak are more common for cases than for deaths. 
Conversely, failure to predict an upswing while numbers are still low, is less severely punished on the natural scale (see forecasts in July in Figure \ref{fig:HUB-model-comparison-ensemble} A, B), as overall absolute errors are low. On the log scale, missing lower inflection points tends to lead to more severe penalties (see panels C and D). One can also observe that on the natural scale, scores tend to track the overall level of the target quantity (compare for example forecasts for March-July with forecasts for September-October in Figure \ref{fig:HUB-model-comparison-ensemble}E, F). On the log scale, scores increase whenever forecasts are far away from the truth in relative terms, regardless of the overall level of observations.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/HUB-pairwise-comparisons.png}
    \caption{Changes in model ratings as measured by relative skill for two-week-ahead predictions. Top row: cases, bottom row: deaths. NEED TO CHANGE THE ANNOTATION LEVELS.}
    \label{fig:HUB-pairwise}
\end{figure}

Evaluating the rank order of forecasts from the ECDC forecast hub we saw that scoring after a log transform altered the order of forecast models. In particular, we note that models that are known to not make use of a exponential error model and to be biased towards under-prediction, such the the MUNI-ARMA model were ranked lower when using a log transform. A submission by the authors of this study, the epiforecasts-EpiNow2 forecast model, was the most impacted by the change to log scale scoring moving from last place for reported cases to 4th place. This makes sense given that it explicitly models errors on an exponential scale, and is relatively unbiased meaning it may be over-penalised due to over-prediction during periods of peak incidence. Interestingly, other models that are growth rate based, such as the LANL-GrowthRate forecaster, do less well after a log-transform. Encouragingly for the ECDC forecast Hub the Hub ensemble, which is the forecast the organisers suggest forecast consumers make use of, remains one of the top forecasts across scoring schemes and indeed ranks higher for reported cases when a log transform is used.

>>>>

Probabilistic forecasts \citep{heldProbabilisticForecastingInfectious2017} play an important role in decision-making in epidemiology and public health \citep{reichCollaborativeMultiyearMultimodel2019, funkShorttermForecastsInform2020, cramerEvaluationIndividualEnsemble2021, bracherShorttermForecastingCOVID192021, europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}, as well as other areas as diverse as economics \citep{timmermannForecastingMethodsFinance2018, elliottForecastingEconomicsFinance2016} or meteorology \citep{gneitingWeatherForecastingEnsemble2005, kukkonenReviewOperationalRegionalscale2012}. Epidemiological modelling in particular has received widespread attention during the COVID-19 pandemic. Evaluations of forecasts can provide feedback for forecasters and researchers to improve their models and train ensembles, and help decision makers distinguish good from bad predictions and choosing forecasters and models that should inform future decisions.

Probabilistic forecasts are usually evaluated using so-called proper scoring rules \citep{gneitingStrictlyProperScoring2007}, which return a numerical score as a function of the forecast and the observed data. Forecasters, in expectation, optimise their score by providing a predictive distribution that is equal to the data-generating distribution, and are penalised if they fail to do so. 
Examples of proper scoring rules that have been used to assess epidemiological forecasts are the Continuous Ranked Probability Score~\citep[CRPS,][]{gneitingStrictlyProperScoring2007} or its discrete equivalent, the Ranked Probability Score~\citep[RPS,][]{funk19_assessingperformancereal}}, and the Weighted Interval Score \citep[WIS,][formulas given in Section \ref{wis} in the SI]{bracherEvaluatingEpidemicForecasts2021} for predictive distributions represented by a set of predictive quantiles, used to assess forecasts in COVID-19 forecast hubs in the US \citep{cramerCOVID19ForecastHub2020, cramerEvaluationIndividualEnsemble2021}, Europe \citep{sherrattPredictivePerformanceMultimodel2022}, Germany and Poland \citep{bracherShorttermForecastingCOVID192021, bracherNationalSubnationalShortterm2021}, as well as the US Influenza Forecasting Hub \citep{CdcepiFlusightforecastdata2022}. The WIS and the (C)RPS measure the absolute distance between the predictive distribution and the observed value and can be understood as a generalisation of the absolute error to full predictive distributions (see details in Sections \ref{wis} and \ref{crps} in the SI). For simplicity, we will use "absolute error" and "absolute distance" interchangeably, even though the former applies only to point forecasts and the latter is more appropriate for predictive distributions.

Infectious processes are commonly modelled around the concept of the reproduction number, the average number of new cases generated by each case in the population.
In the absence of changes in immunity, behaviour or other factors that may affect the intensity of transmission, the reproduction number would be expected to remain approximately constant.
In that case, the number of new infections in the population grows exponentially in time~\citep{dushoff2021_speedstrengthepidemic}.
This behaviour was observed, for example, early in the COVID-19 pandemic in many countries~\citep{pellis21_challengescontrolcovid}.
If case numbers are changing exponentially and the true modelling task revolves around estimating the reproduction number or the corresponding growth rate, evaluating forecasts based on the absolute distance between forecast and observed value rewards underprediction compared to overprediction by the same amount, as these errors grow exponentially with the error on the estimated reproduction number or growth rate.
Instead, if one is to assess the ability of forecasts to assess and forecast the underlying infection dynamics, it may be more appropriate to evaluate errors on the growth rate directly.

Moreover, if forecasts based are evaluated on absolute rather than relative errors whereas in reality errors scale with the level of observations, scores are strongly influenced by the overall order of magnitude of the quantity to forecast.
This makes it difficult compare predictive performance across time or to compare performance across targets that generally occur different orders of magnitudes.
In the example of COVID-19 where case numbers underwent drastic changes over time following the initial emergence, forecast evaluation based on the absolute numbers would be dominated by performance around the peaks, and evaluation based on jointly evaluating the ability to predict numbers of cases, hospitalisation and deaths dominated by cases as they occur at largest numbers.

In this paper, we discuss how log-transforming the forecasts and observations prior to applying the WIS (or CRPS) may be an appropriate way to address the aforementioned issues with evaluating forecasts based on absolute errors. We first outline the motivation for transforming forecasts prior to scoring (section [REF]). We then provide a mathematical intuition of the impact of scoring on the log scale and its interpretation (section [REF]). We illustrate our findings on a series of examples using forecasts submitted to the European COVID-19 Forecast Hub  \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. Finally, we give scoring recommendations, discuss alternative transformations that may be useful in different contexts, and suggest further research avenues on the use of transformed scores in the evaluation of infectious disease forecasts.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{log-transforming forecasts and observations}

Our aim in log-transforming forecasts and observations is to shift the focus of the evaluation in a way that may more appropriate for epidemiological forecasts, while preserving the propriety of the score. Instead of a score representing the magnitude of absolute errors this approach makes it possible to obtain a score which a) measures relative error and at the same time b) provides an approximate measure for how well a forecast captures the multiplicative growth rate of the target quantity. Focusing on relative errors mitigates issues with scores based on absolute errors that are heavily influenced by the order of magnitude of the quantity to forecast. The interpretation of the log-transformed score as an approximate score for a forecast of the growth rate of a given quantity aligns the evaluation with our understanding of how epidemiological processes should be modeled and the kinds of errors models would typically make [CITATION?]. In this paper we focus on the log-transformation, but note that many other transformations may be useful and appropriate (see section \ref{sec:discussion}).
We further focus on the WIS as evaluation metric, given its widespread use throughout the COVID-19 pandemic.

@@

To illustrate the effects of applying the logarithm, let us consider a point forecast $\hat{y}_{t+1}$ for a quantity of interest $y_{t+1}$, such that 
\begin{equation}
y_{t+1} = \hat{y}_{t+1} + \varepsilon_{t+1}.
\end{equation}

The analogue of the WIS / CRPS for point forecasts is the absolute error, and so the score will be determined by the size of the forecast error $\varepsilon_{t+1}$. When taking the logarithm of the forecast and the observation first, then the score is determined by $\varepsilon^*_{t+1}$: 
\begin{equation}
\log y_{t+1} = \log \hat{y}_{t+1} + \varepsilon^*_{t+1}.
\end{equation}
%
This corresponds to evaluating a multiplicative error on the original $y_{t+1}$:
%
\begin{align}
\log y_{t+1} &= \log \hat{y}_{t+1} + \varepsilon^*_{t+1} \Leftrightarrow \\    
y_{t+1} &= \hat{y}_{t+1} \cdot \exp{\varepsilon^*_{t+1}}.    
\end{align}
% %>%

@@

The analogy between the WIS on the log scale and the absolute error of a point forecast on the log scale is slightly inaccurate: While the absolute error on the log scale is exactly symmetric (e.g., predicting 2 instead of 1 would give the same relative error as predicting 0.5), this is not entirely true for the WIS, which is computed for a set of prediction intervals. Due to the fact that upper and lower bounds of individual prediction intervals are affected slightly differently by the log-transformations, small deviations may occur (compare e.g. in Figure \ref{fig:change-in-scores}D the small difference between scores for an observed outcome of $\frac{1}{5}$ and 5).

@@

Computing a score based on the logarithm of the forecast and the observation is also approximately equivalent to scoring a forecast of a multiplicative growth rate of the forecast target, which approximates the more commonly used exponential growth rate. The multiplicative growth rate is defined as
%
\begin{equation}
    g_{t, t+1} = \frac{y_{t+1} - y_t}{y_t},
\end{equation}
%
where $y_{t+1}$ is the forecast target (e.g. reported cases of COVID-19) in the future, $y_t$ is the last known observation and $g_{t, t+1}$ is the growth rate between now ($t$) and $t+1$. 
Using the growth rate, we can express the value of the forecast target in the future as such: 
%
\begin{equation}
y_{t+1} = (1 + g_{t, t+1}) \cdot y_t.
\end{equation}
%

Now consider a forecast of $\log y_{t+1}$, where again, the score is determined by the size of $\varepsilon^*_{t+1}$. Using the fact that for small values of $x$, $\log (1+ x) \approx x$, we can see that scoring forecasts on the log scale is approximately equal to scoring an additive error on the growth rate (on the natural scale), as long as the growth rate is small.
%
\begin{align}
\log y_{t+1}        &= \log \hat{y}_{t+1} + \varepsilon^*_{t+1} \nonumber\\
                    &= \log ((1 + \hat{g}_{t+1}) \cdot y_{t}) + \varepsilon^*_{t+1} \\
                    &= \log (1 + \hat{g}_{t, t+1}) + \log y_t + \varepsilon^*_{t+1} \Leftrightarrow \nonumber \\
\nonumber \\
\varepsilon^*_{t+1}  &= \log y_{t+1} -  \log y_t - \log (1 + \hat{g}_{t, t+1}) \nonumber \\    
                    &= \log \left(\frac{y_{t+1}}{y_t}\right) - \log (1 + \hat{g}_{t, t+1}) \\    
                    &= \log (1 + g_{t, t+1}) - \log (1 + \hat{g}_{t, t+1})\nonumber  \\   
                    &\approx g_{t, t+1} - \hat{g}_{t, t+1} \quad \text{for small differences between } \hat{g}_{t, t+1} \text{ and } g_{t, t+1}. \nonumber
\end{align}

@@

\subsection{Effects on model rankings}
Rankings between different forecasters may change through the log-transformation both when looking at aggregate scores as well as when looking at a single forecast. As an example for the effect on a single forecast, consider two forecasters, A and B. Both issue a single 50\%-prediction interval for a target which later resolves as 1. Forecaster A issues the interval [0.5, 2], while forecaster B issues [0.9. 2.5]. On the natural scale, the score would equal the dispersion of the forecast, i.e. the length of this interval (since the observed value falls within the prediction interval). Forecaster A would receive a score of $2 - 0.5$ = 1.5, beating forecaster B who would receive a score of $2.5 - 0.9 = 1.6$. When we transform the forecast, forecaster A receives a score of $\log (\frac{2}{0.5}) = 1.39$, while forecaster B obtains a score of $\log (\frac{2.6}{0.9}) = 1.06$ and now wins over forecaster A. The main difference between forecaster A and B is that forecaster A has issued a prediction interval ([0.5, 2]) that was more symmetric around the true value than the interval issued by forecaster B ([0.9. 2.6], which was more skewed). This means that in relative terms, Forecaster B was noticeably closer to the true value with the lower bound of her prediction interval, while only being slightly further away with the upper interval. This implies that scores on the log scale may treat (one-sided) outlier forecasts more leniently.

% PARAGRAPH NEEDS SOME WORK
Overall model rankings would be expected to differ even more when scores are averaged across multiple forecasts or targets. The change in rankings of aggregate scores is not mainly driven by the kinds of changes in model rankings for single forecasts just discussed. Rather, as observations from exponential processes are likely to be on very different absolute scales, large observations will account for the majority of absolute score but will not dominate relative scores in the same way. When aggregating scores across metrics with different scales, for example reported cases, and hospitalisations, even an ideal (i.e. perfect) forecaster will make much larger errors when predicting case numbers than when predicting hospitalisations. Evaluating forecasts based on relative errors may help with comparing performance across different targets. However, log-transforming forecasts and observations may also result in the opposite extreme because small absolute errors (e.g. predicting 9, rather than 3 deaths) may be large in relative terms if the quantity to forecast is very small. This can be exacerbated when forecasts are restricted to discrete values, where relative steps between possible values become greater closer to zero.

@@

The log-transformation is permissible (in the sense that it preserves propriety of the score), because it is a strictly monotonic transformation. Even though actual rankings between models may change, forecasters will  still minimise her score if they report a predictive distribution that is equal to the data-generating distribution. The order of the operations matters, and applying the log-transformation after scores have been computed, i.e. computing $\log S(F, y)$ results in an improper score. This is because taking the logarithm of the WIS / CRPS results in a score that does not penalise outliers enough and therefore incentivises overconfident predictions. We illustrate this point using simulated data in Figure \ref{fig:log-improper}, where it can easily be seen that overconfident models perform best in terms of the log WIS.

@@

In practice, one issue with the log-transformation is that it cannot readily be applied to negative numbers or zero values. In addition, it may difficult to reliably evaluate relative errors when dealing with small discrete values. In an epidemiological setting that involves count data, negative values should likely be omitted entirely. One solution to deal with zeroes and small values is to also exclude those from ongoing analysis. An alternative is to add a small quantity, such as 1, to all observations and predictions before taking the logarithm as is common practice when log-transforming counts. This represents a strictly monotonic transformation and therefore preserves propriety of the resulting score. The choice of the number to add influences scores and rankings, as measures of relative errors shrink when adding a constant to the forecast and the observation. Adding something to the forecasts and observations changes scores for forecasts of small quantities most, as relative errors shrink more the smaller the original value before adding a constant. In principle, it would also be possible to exploit the difference in how scores are affected in order to equalise scores for forecasts of quantities across different scales by adding a larger number (e.g. 100 or 10,000) if average scores are dominated too strongly by forecasts for small quantities.

@@

As an empirical example for evaluating forecasts on the natural and on the log scale we use forecasts from the European Forecast Hub \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. 
The European COVID-19 Forecast Hub is one of several COVID-19 Forecast hubs (together with a Hub in the US \citep{cramerEvaluationIndividualEnsemble2021} and one in Germany and Poland \citep{bracherShorttermForecastingCOVID192021} that systematically collects, aggregates and evaluates forecasts of several COVID-19 targets created by different teams every week. Forecasts are made one to four weeks ahead into the future and follow a quantile-based format with a set of 22 quantiles plus the median ($0.01, 0.025, 0.05, ..., 0.5, ... 0.95, 0.975, 0.99$).

@@

In addition to the WIS we use pairwise comparisons \citep{cramerEvaluationIndividualEnsemble2021} to evaluate the relative performance of models across countries in the presence of missingness. In a first step, score ratios are computed for all pairs of models by taking the set of overlapping forecasts between the two models and dividing the score of one model over the score achieved by the other model. The relative skill for a given model is then obtained by taking the geometric mean of all score ratios which involve that model. Low values are better, and the average model receives a relative skill score of 1.

@@

Across the dataset, the average number of observed cases and deaths varied considerably by location and target type (see Figure \ref{fig:HUB-mean-locations}A and B). On the natural scale, scores also varied considerably across targets (see Figure\ref{fig:HUB-mean-locations}D) and locations (see Figure\ref{fig:HUB-mean-locations}C). On the log scale, scores were more evenly distributed between targets (see Figure\ref{fig:HUB-mean-locations}D) and locations (see Figure\ref{fig:HUB-mean-locations}C). Both on the natural scale as well to a slightly lesser extent on the log scale, scores increased considerably with increasing forecast horizon (see Figure \ref{fig:HUB-mean-locations}E). We hypothesise that this increase in scores across horizons represents the relative difficulty to forecast values into the future, which was noticeable both on the natural as well as the logarithmic scale.

@@

As expected on the natural scale, scores correlate strongly with the average number of observed cases and deaths (Spearman rank correlation: 0.96 and 0.97) in a given country (see Figure\ref{fig:HUB-mean-locations}A, B).
On the log scale, the correlation is much weaker and slightly negative, at least in terms of rank correlation (Spearman correlation: -0.33 and -0.36), implying a tendency towards larger scores in countries with lower mean incidences.

@@

For \textit{individual} forecasts, rankings between models for single forecasts are mostly preserved, with differences increasing across forecast horizons (see Figure \ref{fig:HUB-cors}B). When evaluating performance \textit{averaged across} different forecasts and forecast targets, relative skill scores of the models change considerably. The change is stronger for cases than for deaths (Figure \ref{fig:HUB-cors}C) and possibly tends to increase with increasing forecast horizon.

When comparing examples of forecasts on the natural scale with those on the log scale (see Figures \ref{fig:HUB-model-comparison-ensemble}, \ref{fig:HUB-model-comparison-baseline}, \ref{fig:HUB-model-comparison-epinow}) a few interesting patterns emerge. Missing the peak, i.e. predicting increasing numbers while actual observations are already falling, tends to contribute a lot to overall scores on the natural scale (see forecasts in May in Figure \ref{fig:HUB-model-comparison-ensemble}A, B). On the log scale, these have less of an influence, as errors are smaller in relative terms (see \ref{fig:HUB-model-comparison-ensemble}C, D). We hypothesise that the lower correlation between skill scores for cases (compared to the correlation of scores for deaths) as displayed in Figure \ref{fig:HUB-cors}C is related to the fact that outlier forecasts missing the peak are more common for cases than for deaths, and therefore relative skill scores are more strongly affected for cases. 
Conversely, failure to predict an upswing while numbers are still low, is less severely punished on the natural scale (see forecasts in July in Figure \ref{fig:HUB-model-comparison-ensemble} A, B), as overall absolute errors are low. On the log scale, missing lower inflection points tends to lead to more severe penalties (see Figure \ref{fig:HUB-model-comparison-ensemble}C, D)). One can also observe that on the natural scale, scores tend to track the overall level of the target quantity (compare for example forecasts for March-July with forecasts for September-October in Figure \ref{fig:HUB-model-comparison-ensemble}E, F). On the log scale, scores do not exhibit this behaviour and rather increase whenever forecasts are far away from the truth in relative terms, regardless of the overall level of observations.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/HUB-pairwise-comparisons.png}
    \caption{Changes in model ratings as measured by relative skill for two-week-ahead predictions. Top row: cases, bottom row: deaths. NEED TO CHANGE THE ANNOTATION LEVELS.}
    \label{fig:HUB-rank-order}
\end{figure}
